# 1.32 R: Simulate flipping three fair coins and counting the number of heads X.

## (a) Use your simulation to estimate P(X = 1) and E(X).

```{r}
flip3 <- function() {
    sum(sample(0:1, 3, replace = TRUE))
}
```

```{r}
n <- 10000
x <- replicate(n, flip3())

```

```{r}
print(sum(x) / n)

```

```{r}
is_1 <- (x == 1)
print(sum(is_1) / n)
```

So $E[x]$ is around $1.5$. And $P(X=1)$ is around $0.377$.

## (b) Modify the above to allow for a biased coin where P(Heads)=3∕4.

```{r}
flip3_bias <- function() {
    naive <- sample(0:3, 3, replace = TRUE)
    is_heads <- (naive != 0)
    sum_heads <- sum(is_heads)
    return(sum_heads)
}
```


```{r}
n <- 10000
x <- replicate(n, flip3_bias())

```

```{r}
print(sum(x) / n)

```

```{r}
is_1 <- (x == 1)
print(sum(is_1) / n)
```




So $E[x]$ is around $2.26$. And $P(X=1)$ is around $0.1368$.




# 1.35 R: See the script file gamblersruin.R. A gambler starts with a $60 initial stake.
 (a) The gambler wins, and loses, each round with probability p = 0.50. Simu
late the probability the gambler wins $100 before he loses everything.
 (b) Thegamblerwinseachroundwithprobability p = 0.51.Simulatetheprob
ability the gambler wins $100 before he loses everything.